Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-30 Draft/Draft.Rmd
a bit more of intro

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019]. Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.

Several studies have evaluated the structure of plant-pollinator interactions. These studies have found common structural properties across networks that can help the understanding of the determinats of biodiversity [@bastolla2009]. One of the major findings is the nested structure of mutualistic networks [@bascompte2003] which describes the topological structure where the specialist interact with subgroups of the interacting species of the generalist. Further, the degree distribution (number of links per species) of plant-pollinator networks have been shown to generally follow a power-law truncated distribution [@jordano2003]. Moreover, at the species level ...

>>>>

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019]. Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light on ecological processes not captured by the traditional approaches used in plant-pollinator network studies.

Research of plant-pollinator networks have proven common invariant structural properties across networks. Mutualistic networks tend to be nested [@bascompte2003], the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003] and there is an imbalance with approximately four times more pollinator species than plant species [@vazquez2009]. In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020]. Despite progress in plant-pollinator interactions, indirect interactions such as the competitive and facilitative interactions between plants for pollinators have been rarely investigated [@simmons2020]. However, the recent advances in analytical tools [..To be continued..]
